### 2014-05-21 acks.tex
Zephyr fixes through 1:41 p.m.

I owe much to my time in the Wall Street Journal's late Boston
bureau. My editors Gary Putka and Dan Golden, and my colleague Charles
Forelle, taught me how to develop a nose for investigations and how to
tell a story. Gary's ``dun-colored warren of cubicles'' represented a
journalistic Camelot and was as intellectually challenging as any lab.

@@

To my labmates and ninth floor cohabitants---Katrina LaCurts, Raluca
Ada Popa, Shuo Deng, Lenin Ravindranath, Ravi Netravali, Peter
Iannucci, Tiffany Chen, Amy Ousterhout, Jonathan Perry, Neha Narula,
Austin Clements, Emily Stark, Cody Cutler, Eugene Wu, Dan Ports, Silas
Boyd-Wickizer, and Sheila Marian---thank you for your companionship
and our time together.

>>>>

I owe much to my time in the Wall Street Journal's late Boston
bureau. My editors Gary Putka and Dan Golden, and my colleague Charles
Forelle, taught me how to dig deeper and how to
tell a story. Gary's ``dun-colored warren of cubicles'' represented a
journalistic Camelot and was as intellectually challenging as any lab.

@@

To my labmates and ninth-floor cohabitants---Katrina LaCurts, Raluca
Ada Popa, Shuo Deng, Lenin Ravindranath, Ravi Netravali, Peter
Iannucci, Tiffany Chen, Amy Ousterhout, Jonathan Perry, Neha Narula,
Austin Clements, Emily Stark, Cody Cutler, Eugene Wu, Dan Ports, Silas
Boyd-Wickizer, and Sheila Marian---thank you for your companionship
and our time together.

### 2014-05-21 intro.tex
Zephyr fixes through 1:41 p.m.

This has led to the ``bufferbloat''\cite{bufferbloat} problem:
believing that the transport layer will interpret losses as a signal
to slow down, the network tries to drop packets as rarely as
possible. It has also led to a lack of parallelism in Internet
routing---flows only take one path, even if striping across
multiple paths could yield a speedup---on the grounds that the
transport protocol might interpret out-of-order packets as a
pathology.

>>>>

This has led to the ``bufferbloat''~\cite{bufferbloat} problem:
believing that the transport layer will interpret losses as a signal
to slow down, the network tries to drop packets as rarely as
possible. It has also led to a lack of parallelism in Internet
routing---flows only take one path, even if striping across
multiple paths could yield a speedup---on the grounds that the
transport protocol might interpret out-of-order packets as a
pathology.

### 2014-05-21 remy_design.tex
Fixes to Remy section
Zephyr fixes through 1:41 p.m.

A single evaluation step consists of drawing somewhere between 16 and
100 network specimens from the network model, then simulating the
RemyCC algorithm at each sender an extended length of time on each
network specimen. At the end of the simulation, the objective function
for each sender, given by Equation~\ref{eq:util}, is totaled to
produce an overall figure of merit for the RemyCC. We explore two
cases, $\alpha = \beta = 1$ and $\alpha=2, \delta = 0$. The first case
corresponds to proportional throughput and delay fairness,
maximizing $$U = \log (\mbox{throughput}) - \delta \cdot \log
(\mbox{delay}),$$ with $\delta$ specifying the importance placed on
delay vs.~throughput. The second case corresponds to minimizing the
potential delay of a fixed-length transfer, by maximizing $$U =
-\frac{1}{\mbox{throughput}}.$$

@@

\item \textbf{Improve that action until we can't anymore.} Focus on
  this rule and find the best action for it. Draw at least 16 network
  specimens from the model, and then evaluate roughly 100 candidate
  increments to the current action, increasing geometrically in
  granularity as they get further from the current value. For example,
  evaluate $r \pm 0.01$, $r \pm 0.08$, $r \pm 0.64$, \ldots, taking
  the Cartesian product with the alternatives for $m$ and $b$.

>>>>

A single evaluation step consists of drawing somewhere between 16 and
100 network specimens from the network model, then simulating the
RemyCC algorithm at each sender for an extended length of time on each
network specimen. At the end of the simulation, the objective function
for each sender, given by Equation~\ref{eq:util}, is totaled to
produce an overall figure of merit for the RemyCC. We explore two
cases, $\alpha = \beta = 1$ and $\alpha=2, \delta = 0$. The first case
corresponds to proportional throughput and delay fairness,
maximizing $$U = \log (\mbox{throughput}) - \delta \cdot \log
(\mbox{delay}),$$ with $\delta$ specifying the importance placed on
delay vs.~throughput. The second case corresponds to minimizing the
potential delay of a fixed-length transfer, by maximizing $$U =
-\frac{1}{\mbox{throughput}}.$$

@@

\item \textbf{Improve that action until we can't anymore.} Focus on
  this rule and find the best action for it. Draw at least 16 network
  specimens from the model, and then evaluate roughly 100 candidate
  increments to the current action, increasing geometrically in
  granularity as they get further from the current value. For example,
  evaluate $\tau \pm 0.01$, $\tau \pm 0.08$, $\tau \pm 0.64$, \ldots, taking
  the Cartesian product with the alternatives for $m$ and $b$.

### 2014-05-21 sprout_eval.tex
Zephyr fixes through 1:41 p.m.

For a given trace, there is a lower limit on the 95\%~end-to-end delay
that can be achieved even by an omniscient protocol: one that sends
packets timed to arrive exactly when the network is ready to dequeue
and transmit a packet. This ``omniscient'' protocol will achieve
100\%~of the available throughput of the link and its packets will
never sit in a queue. Even so, the ``omniscient'' protocol will have
fluctuations in its 95\%~end-to-end delay, because the link may have
delivery outages. If the link does not deliver any packets for 5
seconds, there must be at least 5 seconds of end-to-end delay to avoid
a glitch, no matter how smart the protocol is.\footnote{If packets are
  not reordered by the network, the definition becomes simpler. At
  each instant that a packet arrives, the end-to-end delay is equal to
  the delay experienced by that packet. Starting from this value, the
  end-to-end delay increases linearly at a rate of 1 s/s, until the
  next packet arrives. The 95th percentile of this function is the
  95\%~end-to-end delay.}

The difference between the 95\%~end-to-end delay measured for a
particular protocol and for an ``omniscient'' one is known as the
\emph{self-inflicted delay}. This is the appropriate figure to assess
a real-time interactive protocol's ability to compromise between
throughput and the delay experienced by users.

>>>>

For a given trace, there is a lower limit on the 95\%~end-to-end delay
that can be achieved even by an omniscient protocol: one that sends
packets timed to arrive exactly when the network is ready to dequeue
and transmit a packet. This protocol will achieve
100\%~of the available throughput of the link and its packets will
never sit in a queue. Even so, the omniscient protocol will have
fluctuations in its 95\%~end-to-end delay, because the link may have
delivery outages. If the link does not deliver any packets for 5
seconds, there must be at least 5 seconds of end-to-end delay to avoid
a glitch, no matter how smart the protocol is.\footnote{If packets are
  not reordered by the network, the definition becomes simpler. At
  each instant that a packet arrives, the end-to-end delay is equal to
  the delay experienced by that packet. Starting from this value, the
  end-to-end delay increases linearly at a rate of 1 s/s, until the
  next packet arrives. The 95th percentile of this function is the
  95\%~end-to-end delay.}

The difference between the 95\%~end-to-end delay measured for a
particular protocol and for an omniscient one is known as the
\emph{self-inflicted delay}. This is the appropriate figure to assess
a real-time interactive protocol's ability to compromise between
throughput and the delay experienced by users.
